DSCI 445 - Utilizing Machine Learning for Algae Predictions

### 2020-12-10 slides.Rmd

```{python, include=FALSE}
from plots import *
=======
```{r setup, include=FALSE}
library(tidyverse)
library(tmap)
library(tmaptools)
library(USAboundaries)
library(sf)
knitr::opts_chunk$set(echo = FALSE)
>>>>>>> Stashed changes
```

@@

![](HT_Monthly.jpeg){width=1000px}

@@

![](HT_Obs.jpeg){width=1000px}

@@

![](ht_color_dist.jpeg){width=1000px}

@@

We can see that Horsetooth is more green and has higher wavelengths in the summer months.
This trend is not specific to Horsetooth, as algae blooms will cause this. This trend is why we only care about summer months.

![](HT_Climatology.jpeg){width=1000px}

## What does that mean for the summer months, though?

@@

![](ht_color_over_time.jpeg){width=1000px}

@@

- We can interpret residuals as the **negative gradient** of the total loss defined before.
- Like AdaBoost, we update the prediction function, but now, we update $F(\cdot)$ based on the negative gradient of our total loss.
- This algorithm can handle different loss functions, with different properties, making it very flexible.
- Here, we use the default implementation in `scikit-learn`, which has a least-squares loss function:

>>>>

```{python, include=FALSE}
from plots import *
```

@@

![](HT_Monthly.jpeg)

@@

![](HT_Obs.jpeg)

@@

![](ht_color_dist.jpeg)

@@

We can see that Horsetooth is more green and has higher wavelengths in the
summer months. This trend is why we only care about summer months.

![](HT_Climatology.jpeg)

## Summer Months

@@

![](ht_color_over_time.jpeg)

## Summer Months

- Over time, during the summer, Horsetooth is becoming more blue. 
- This is not the case for all reservoirs; some are actually becoming more
  green. 
- The greener they are, the more suspected algae is in the water.

![](ht_color_over_time.jpeg)

@@

- We can interpret residuals as the **negative gradient** of the total loss
  defined before.
- Update $F(\cdot)$ based on the negative gradient of our total loss.
- This algorithm can handle different loss functions, with different
  properties, making it very flexible.
- Here, we use the default implementation in `scikit-learn`, which has a
  least-squares loss function:
